### 2013-03-28 doc/sosp13/evaluation.tex
pe2

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($~$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context switch
is around 75ns.

>>>>

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($\approx$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context switch
is around 75ns.
